---
title: "Incarceration-ass3"
author: "Ha Eun Lee"
date: "11/18/2021"
output: html_document
---

```{r setup, include=FALSE}
incarceration <- read.csv("/Users/haeun/Desktop/incarceration_trends.csv")
knitr::opts_chunk$set(echo = TRUE)
source("analysis.r")
library("dplyr")
library("ggplot2")
library("tidyverse")
library("maps")
library("mapproj")
```


## Introduction and Summary information
1. The size of the data set is `r data_description$observations`.
2. The range of years the data set covers is `r data_description$year`, and the most recent year in the data is 2018, which is 3 years ago.
3. The total population in the data set is `r data_description$total_pop_no_year`.
4. The total number of incarcerated in the data set is `r data_description$total_incarcerated_pop`.
5. The total population of incarceration tends to decrease in about 2015. I believe that this is because of some strict policies on crime. 


## Trends over time chart
- The incarcerated population is getting bigger as years pass, but it has decreased slightly since 2015.

```{r incarceration_trends_plot, echo=FALSE}
incarceration_over_time_plot
```


## Variable comparison chart
- In those 10 states, black incarceration rate is much higher than its total incarceration rate.

```{r top_10_black_incarceration_plot, echo=FALSE}
top_10_black_incarceration_plot
```


## Map 
- The ratio of black and white in Lincoln county is the highest. I think this could be due to higher black population in Lincoln county compare to other counties in WA. 

```{r racial_incarceration_discrepancy_map_plot, echo=FALSE}
racial_incarceration_discrepancy_map_plot
```